Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-22 WSSSPE3/report/WSSSPE3_review.tex
Section 3: Keynote. Dropped 'circumpolar'. Too colorful.

WSSSPE3 broke free of the traditional Supercomputing Conference
environment this year, and in Turk's words, it spoke to the fact that scientific
software comes from many different types of inquiries, deployment, strategies
for maintenance, users; and ways of measuring the value of a piece of software.
It appeared to Turk that the supercomputing conferences generally adopt some
top-down approaches, whereas SciPy generally uses more bottom-up systems.
The essential messages
perceived were also often circumpolar: \katznote{this means ``situated around or inhabiting one of the earth's poles'' - not sure this is the right word} software getting harder in supercomputing
communities with exascale computing and optimization issues in mind, but software becoming better in the
SciPy group with emerging tools such as Jupiter and productivity packages for research workflow.
Admitting such comparisons are somewhat unfair generalizations, Turk reminded the
audience that the different approaches bring different types of ideas to the
table, but he welcomed WSSSPE3 being conducted outside existing preconceptions.

>>>>

WSSSPE3 broke free of the traditional Supercomputing Conference environment this
year, and in Turk's words, it spoke to the fact that scientific software comes
from many different types of inquiries, deployment, strategies for maintenance,
users; and ways of measuring the value of a piece of software. It appeared to
Turk that the supercomputing conferences generally adopt some top-down
approaches, whereas SciPy more often than not uses more bottom-up systems. The essential
messages perceived were also often polar: software getting harder in
supercomputing communities with exascale computing and optimization issues in
mind, but software becoming better in the SciPy group with emerging tools such
as Jupiter and productivity packages for research workflow. Admitting such
comparisons are somewhat unfair generalizations, Turk reminded the audience that
the different approaches bring different types of ideas to the table, but he
welcomed WSSSPE3 being conducted outside existing preconceptions.
